---
title: "Basic package workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic package workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(steppedwedge)
```


The `load_sw_data` function takes in raw data and creates a data object that can be accepted by the `plot_sw_design` and `analyze_sw_data` functions. We use the made-up dataframe `sw_data_example` to demonstrate the workflow.

```{r}

data(sw_data_example)

dat <- load_sw_data(
  period = "period",
  cluster_id = "cluster",
  individual_id = NULL,
  treatment = "trt",
  covariates = NULL,
  outcome = "outcome_bin",
  data = sw_data_example
)

```


The `plot_sw_design` function produces a diagram of the stepped wedge design and a summary of the variables.

```{r, fig.width=9, fig.height=8, fig.align = "center"}

plot_dat <- plot_sw_design(dat)

plot_dat

```


The `analyze_sw_data` function analyzes the stepped wedge data. First, we analyze the data using a mixed effects model, with the Time Average Treament Effect (TATE) as the estimand, assuming an Immediate Treatment (IT) effect, passing the `family = "binomial"` and `link = "logit"` arguments to `glmer`. 

```{r}

analysis_1 <- analyze_sw_data(
  dat = dat,
  method = "mixed",
  estimand = "TATE", 
  time_varying_assumption = "IT",
  family = "binomial",
  link = "logit")

analysis_1$model

```


Repeat the analysis, but using GEE rather than a mixed model.

```{r}

analyze_sw_data(
  dat = dat,
  method = "GEE",
  estimand = "TATE", 
  time_varying_assumption = "IT",
  family = "binomial",
  link = "logit")

```

