---
title: "Basic package workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic package workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(steppedwedge)
```

```{r, include = FALSE}
# Including this twice (once here with include=F) avoids a bug having to do with dplyr and pkgdown
data(sw_data_example)
dat <- load_data(
  time = "period",
  cluster_id = "cluster",
  individual_id = NULL,
  treatment = "trt",
  outcome = "outcome_bin",
  data = sw_data_example
)
```

# Loading data

The `load_data` function takes in raw data and creates a data object that can be accepted by the `plot_design` and `analyze` functions. We use the made-up dataframe `sw_data_example` to demonstrate the workflow.

```{r}
data(sw_data_example)
head(sw_data_example)

dat <- load_data(
  time = "period",
  cluster_id = "cluster",
  individual_id = NULL,
  treatment = "trt",
  outcome = "outcome_bin",
  data = sw_data_example
)
```

# Plotting the design

The `plot_design` function produces a diagram of the stepped wedge design and a summary of the variables.

```{r, fig.width=9, fig.height=8, fig.align = "center"}
plot_dat <- plot_design(dat)

print(plot_dat)
```

# Analyzing the data

The `analyze` function analyzes the stepped wedge data. First, we analyze the data using a mixed effects model, with the Time Average Treament Effect (TATE) as the estimand, assuming an Immediate Treatment (IT) effect, passing the `family = "binomial"` and `link = "logit"` arguments to `glmer`. 
## Binary outcome

```{r}
analysis_1 <- analyze(
  dat = dat,
  method = "mixed",
  estimand_type = "TATE", 
  exp_time = "IT",
  family = binomial,
  re = c("clust", "time")
)

print(analysis_1)
```

Repeat the analysis, but including a random effect for cluster only, not for cluster-time interaction.

```{r}
analysis_1b <- analyze(
  dat = dat,
  method = "mixed",
  estimand_type = "TATE", 
  exp_time = "IT",
  family = binomial,
  re = "clust"
)

print(analysis_1b)
```


Repeat the analysis, but using GEE rather than a mixed model.

```{r}
analysis_2 <- analyze(
  dat = dat,
  method = "GEE",
  estimand_type = "TATE", 
  exp_time = "IT",
  family = binomial,
  corstr = "exchangeable"
)

print(analysis_2)
```


Mixed model, with Time Average Treament Effect (TATE) as the estimand, using an Exposure Time Indicator (ETI) model.

```{r}
analysis_3 <- analyze(
  dat = dat,
  method = "mixed",
  estimand_type = "TATE", 
  exp_time = "ETI",
  family = binomial
)

print(analysis_3)
```


Mixed model, with Time Average Treatment Effect (TATE) as the estimand, using a Natural Cubic Splines (NCS) model.

```{r}
analysis_4 <- analyze(
  dat = dat,
  method = "mixed",
  estimand_type = "TATE", 
  exp_time = "NCS",
  family = binomial
)

print(analysis_4)
```


## Continuous outcome

Mixed model, with Time Average Treament Effect (TATE) as the estimand, using a Natural Cubic Splines (NCS) model.

```{r}

dat_cont <- load_data(
  time = "period",
  cluster_id = "cluster",
  individual_id = NULL,
  treatment = "trt",
  outcome = "outcome_cont",
  data = sw_data_example
)

analysis_6 <- analyze(
  dat = dat_cont,
  method = "mixed",
  estimand_type = "TATE", 
  exp_time = "NCS",
  family = gaussian
)

print(analysis_6)
```

## Binomial outcome

When loading data where the outcome is binomial, specify the names of the "# of successes" and "# of trials" variables as the `outcome` argument.

```{r}

dat_binom <- load_data(
  time ="period",
  cluster_id = "cluster",
  individual_id = NULL,
  treatment = "trt",
  outcome = c("numerator", "denominator"),
  data = sw_data_example_binom
)

```


Mixed model, with Time Average Treament Effect (TATE) as the estimand, using an Exposure Time Indicator (ETI) model.

```{r}

analysis_binom <- analyze(
  dat = dat_binom,
  method = "mixed",
  family = binomial,
  estimand_type = "TATE", 
  exp_time = "ETI")

print(analysis_binom)

```


# Plotting effect curves

The `plot_effect_curve` function plots effect estimates by exposure time for one or more `analyze` objects. 

```{r}

IT_model <- analyze(
  dat = dat_cont, method = "mixed", estimand_type = "TATE",
  estimand_time = c(1, 4), exp_time = "IT"
)
ETI_model <- analyze(
  dat = dat_cont, method = "mixed", estimand_type = "TATE", 
  estimand_time = c(1, 4), exp_time = "ETI"
)
NCS_4_model <- analyze(
  dat = dat_cont, method = "mixed", estimand_type = "TATE",
  estimand_time = c(1, 4), exp_time = "NCS", 
  advanced = params(n_knots_exp = 4)
)

plot_effect_curves(IT_model, NCS_4_model, ETI_model, facet_nrow = 1)


```

# Plotting cluster charts

The `plot_clusters` function plots actual and predicted outcomes for each cluster by calendar time for an `analyze` object.

## Continuous outcome

For continuous outcomes, the actual outcomes are jittered, with the predicted outcomes represented by the plotted line:

```{r, fig.height = 8}

plot_clusters(analysis_6, ncol = 3)

```

## Binary outcome

For binary outcomes, the observed probability for each cluster period is plotted as a point, with the predicted probabilities represented by the plotted line:

```{r, fig.height = 8}

plot_clusters(analysis_4, ncol = 3)

```


